### 2022-03-24 draft.tex
Deploying to gh-pages from @ emuise/ms-assessingRepresentation@9c39515a926eb3a7d26c7512b780efb8fd61fc67 🚀

\hypertarget{ecosystems-land-cover-and-disturbances-1}{%
\subsubsection{Ecosystems, Land Cover, and
Disturbances}\label{ecosystems-land-cover-and-disturbances-1}}

@@

\hypertarget{forest-structural-attributes-1}{%
\subsubsection{Forest Structural
Attributes}\label{forest-structural-attributes-1}}

@@

** 14.03 **\strut

@@

** 13.11 **\strut

@@

** -7\% **\strut

@@

** 61.8\% **\strut

@@

** 58.71\% **\strut

@@

** -5.26\% **\strut

@@

** 23.00 **\strut

@@

** 21.58 **\strut

@@

** -6.59\% **\strut

@@

** 0.31 **\strut

@@

** 0.33 **\strut

@@

** 6.35\% **\strut

@@

** 89.38\% **\strut

@@

** 83.69\% **\strut

@@

** -6.79\% **\strut

@@

** 61.7\% **\strut

@@

** 64.97\% **\strut

@@

** 5.04\% **\strut

@@

** 68.17\% **\strut

@@

** 62.07\% **\strut

@@

** -9.83\% **\strut

@@

** 22.53 **\strut

@@

** 21.06 **\strut

@@

** -6.98\% **\strut

@@

** 19.42 **\strut

@@

** 18.31 **\strut

@@

** -6.07\% **\strut

@@

** 57.92\% **\strut

@@

** 48.93\% **\strut

@@

** -18.36\% **\strut

@@

** 19.88 **\strut

@@

** 18.03 **\strut

@@

** -10.24\% **\strut

@@

** 62.24\% **\strut

@@

** 67.25\% **\strut

@@

** 7.45\% **\strut

@@

\begin{figure}
\hypertarget{fig:structure-3d-scatter}{%
\centering
\includegraphics{figures/fstruct_zscores.png}
\caption{Z-Scores of forest structural attributes in PA, UA, and their
differences across BEC zones in BC.}\label{fig:structure-3d-scatter}
}
\end{figure}

>>>>

\hypertarget{ecosystems-land-cover-and-disturbances-1}{%
\subsection{Ecosystems, Land Cover, and
Disturbances}\label{ecosystems-land-cover-and-disturbances-1}}

@@

\hypertarget{forest-structural-attributes-1}{%
\subsection{Forest Structural
Attributes}\label{forest-structural-attributes-1}}

@@

\textbf{14.03}\strut

@@

\textbf{13.11}\strut

@@

\textbf{-7\%}\strut

@@

\textbf{61.8\%}\strut

@@

\textbf{58.71\%}\strut

@@

\textbf{-5.26\%}\strut

@@

\textbf{23.00}\strut

@@

\textbf{21.58}\strut

@@

\textbf{-6.59\%}\strut

@@

\textbf{0.31}\strut

@@

\textbf{0.33}\strut

@@

\textbf{6.35\%}\strut

@@

\textbf{89.38\%}\strut

@@

\textbf{83.69\%}\strut

@@

\textbf{-6.79\%}\strut

@@

\textbf{61.7\%}\strut

@@

\textbf{64.97\%}\strut

@@

\textbf{5.04\%}\strut

@@

\textbf{68.17\%}\strut

@@

\textbf{62.07\%}\strut

@@

\textbf{-9.83\%}\strut

@@

\textbf{22.53}\strut

@@

\textbf{21.06}\strut

@@

\textbf{-6.98\%}\strut

@@

\textbf{19.42}\strut

@@

\textbf{18.31}\strut

@@

\textbf{-6.07\%}\strut

@@

\textbf{57.92\%}\strut

@@

\textbf{48.93\%}\strut

@@

\textbf{-18.36\%}\strut

@@

\textbf{19.88}\strut

@@

\textbf{18.03}\strut

@@

\textbf{-10.24\%}\strut

@@

\textbf{62.24\%}\strut

@@

\textbf{67.25\%}\strut

@@

\textbf{7.45\%}\strut

@@

\includegraphics{figures/fstruct_zscores.png}
\{\#fig:structure-3d-scatter\}
